Implementation of a Fuzzy Rule-Based Classifier using Genetic Algorithms

### 2017-12-08 Article/article.tex
Adding checkRules

\section{Fuzzy Logic}
\subsection{Classification model for fuzzy rules}
For each of these attributes $x_{i}(i=1\cdots n)$ there is three fuzzy sets that are denoted A(i,S), A(i,M), A(i,L), respectively for Small, Medium and Large.
Let's define \textbf{p} as the mapping function from $\{1\cdots s(s\leq4)\}$ to $\{1\cdots4\}$, with $\forall x\neq y, p(x)\neq p(y)$. We use that function to express that not all parameters are needed in a rule.
Thus we can generalise rules as follow :

>>>>

Genetic Algorithm is used to design the Knowledge Base of our Fuzzy System, which is its data base and its rule base.

There is two type of GA rule based classifier : Pittsburgh approach and the Michigan approach one. Pittsburgh : Each chromosome is a rule set. Michigan : each chromosome is a rule, the system evolve as a whole. We decided to use the Pittsburgh approach as it was more intuitive for us to build.

Genetic Algorithm can be used to various part of a fuzzy system:

Tuning the membership function, inference parameters.
Rule learning
Rule selection

\section{Fuzzy Logic}

A fuzzy rulebased system has two components: the Knowledge Base adn the Inference System.

Knowledge Base : storing the available knowledge in the form of fuzzy rules
Inference system : applying a fuzzy reasoning methodon the inputs and the KB rules to give a system output.

Knowledge base is usually obtained from expert knowledge, but also by machine learning since the field emerged in the 80s.

>Data base:
Granularity (nb of ling terms/labels)/ var
Membership functions associated ot the labels
>Rule Base: fuzzy rule composition

KB is composed of RB and DB
RB: Rule set, DB: Membership funct

input>fuzzification interface>inference mechanism (applying RB \& DB)>Defuzzification Interface> output

Inference System is set up by choosing the fuzzy operator for each component (conjunction, implication, defuzzifier, etc...)

\subsection{Classification model for fuzzy rules}
For each of these attributes $x_{i}(i=1\cdots n)$ there is three fuzzy sets that are denoted A(i,S), A(i,M), A(i,L), respectively for Small, Medium and Large.
Let's define \textbf{p} as the mapping function from $\{1\cdots s(s\leq4)\}$ to $\{1\cdots4\}$, with $\forall x\neq y, p(x)\neq p(y)$. We use that function to express that not all parameters are needed in a rule.
Thus we can generalise rules as follow :
